Machine learning enhanced empirical potentials for metals and alloys

### 2020-05-20 doc/papers/ml-eam/manuscript.tex
Minor update.

For the second step, only very few specific 
structures are needed to form physical constraints. Thus, the batching scheme is 
no longer a pre-requiste. Instead, we use the codes of the 'prediction' phase of 
VAP for flexibility \cite{TensorAlloy}. For each type of physical constraint of 
each selected crystal structure, an independent computation graph shall be 
generated by reusing the model parameters. This can be easily achieved within 
our VAP framework. Hence, the complicated derivatives of the losses with respect 
to the model parameters can be solved by TensorFlow automatically.
For example, for the Ni-Mo system, if we select the elastic constants of $c_11$, 
$c_22$ and $c_44$ of fcc Ni and bcc Mo, and the Rose EOS of fcc Ni and bcc Mo as 
the physical constraints, thereshould be $2 \times 2$ separate computation 
graphs (\textrm{Elastic/fcc/Ni, Elastic/bcc/Mo, Rose/fcc/Ni, Rose/bcc/Mo}) under 
the scope 'Constraint'.

>>>>

For the second step, only very few specific 
structures are needed to form physical constraints. Thus, the batching scheme is 
no longer a pre-requiste. Instead, we use the codes of the 'prediction' phase of 
VAP for flexibility \cite{TensorAlloy}. For each type of physical constraint of 
each selected crystal structure, an independent computation graph shall be 
generated by reusing the model parameters. This can be easily achieved within 
our VAP framework. Hence, the complicated derivatives of the losses with respect 
to the model parameters can be solved by TensorFlow automatically.
For example, for the Ni-Mo system, if we select the elastic constants of 
$c_{11}$, $c_{22}$ and $c_{44}$ of fcc Ni and bcc Mo, and the Rose EOS of fcc 
Ni and bcc Mo as the physical constraints, there should be $2 \times 2$ separate 
computation graphs (\textrm{Elastic/fcc/Ni, Elastic/bcc/Mo, Rose/fcc/Ni, 
Rose/bcc/Mo}) under the scope 'Constraint'.
